Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-07 measurements.tex
Energy per bit done. Results done!

\subsubsection{Decoding}
In Figs.~\ref{fig:dec_ene_rasp1_gen_gf2}, \ref{fig:dec_ene_rasp1_gen_gf256},
\ref{fig:dec_ene_rasp1_packet_gf2} and \ref{fig:dec_ene_rasp1_packet_gf256} 
we show the encoding energy per bit consumption for the \ac{Raspi} 1.
Again, we notice very similar behavior and trends as previously
reviewed for the encoding energy per bit expenditure. In this case,
we focus on performance among the coding schemes since the behavior 
and trends were previously explained for the encoding case.
%
\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_generation_size_Rasp_Binary_decoder_1600.eps}
        \caption[]%
        {{\small Energy per bit vs. Generation size for $q = 2$}}
        \label{fig:dec_ene_rasp1_gen_gf2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_generation_size_Rasp_Binary8_decoder_1600.eps}
        \caption[]%
        {{\small Energy per bit vs. Generation size for $q = 2^8$}}
        \label{fig:dec_ene_rasp1_gen_gf256}
    \end{subfigure}
    \vskip\baselineskip
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_symbol_size_Rasp_Binary_decoder_128.eps}
        \caption[]%
        {{\small Energy per bit vs. Packet size for $q=2,\ g=128$}}
        \label{fig:dec_ene_rasp1_packet_gf2}
    \end{subfigure}
    \quad
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_symbol_size_Rasp_Binary8_decoder_128.eps}
        \caption[]%
        {{\small Energy per bit vs. Packet size for $q=2^8,\ g=128$}}
        \label{fig:dec_ene_rasp1_packet_gf256}
    \end{subfigure}
    \caption[]
    {\small Decoder energy measurements for the \ac{Raspi} 1}
    \label{fig:dec_ene_rasp1}
\end{figure*}
%
Some differences occurs due to nature of decoding. In this situation,
the reception of \ac{l.d.} coded packets just increases the decoding
delay, therefore reducing the performance of some coding schemes
in terms of the energy per bit consumption. For example,

\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_generation_size_Rasp_v2_Binary_decoder_1600.eps}
        \caption[]%
        {{\small Energy per bit vs. Generation size for $q = 2$}}
        \label{fig:dec_ene_rasp2_gen_gf2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_generation_size_Rasp_v2_Binary8_decoder_1600.eps}
        \caption[]%
        {{\small Energy per bit vs. Generation size for $q = 2^8$}}
        \label{fig:dec_ene_rasp2_gen_gf256}
    \end{subfigure}
    \vskip\baselineskip
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_symbol_size_Rasp_v2_Binary_decoder_128.eps}
        \caption[]%
        {{\small Energy per bit vs. Packet size for $q=2,\ g=128$}}
        \label{fig:dec_ene_rasp2_packet_gf2}
    \end{subfigure}
    \quad
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_symbol_size_Rasp_v2_Binary8_decoder_128.eps}
        \caption[]%
        {{\small Energy per bit vs. Packet size for $q=2^8,\ g=128$}}
        \label{fig:dec_ene_rasp2_packet_gf256}
    \end{subfigure}
    \caption[]
    {\small Decoder energy measurements for the \ac{Raspi} 2}
    \label{fig:dec_ene_rasp2}
\end{figure*}

\subsection{Multicore Network Coding}
\label{subs:multicore-network-coding}

The authors implemented the algorithm described in
Section~\ref{sub:implementation-multicore} on the \ac{Raspi} 2 model,
which features four ARMv7 cores in a Broadcom BCM2836 \ac{SOC}
with a 900 MHz clock. Each core has a 32 KiB L1 data cache and 32 KiB
L1 instruction cache. The cores share a 512 KiB L2 cache. All the
measured results, including the baseline results, were obtained with
NEON-enabled code adapted from the Fifi library [\textbf{Fifi reference}].
The \ac{Raspi} 2 has a NEON extension instruction set which provides
an 128-bit \ac{SIMD} instructions that speed the computations.
Figures~\ref{enc_dec1024}, \ref{enc_dec128} and
\ref{enc_dec16} show the encoding and decoding goodput in MB per
second for different generation sizes, $g = [1024, 128, 16]$
respectively. The size of each coded packet was fixed to $1536$~bytes
since that is the typical size of an Ethernet frame. The blocked operations
were performed dividing the matrices in squared sub-blocks of
$16,\ 32\ ,\ 64,\ldots,\ 1024$ operands (words in the Galois field) in
height and width. The figures show only block sizes of
$16 \times 16$, $32 \times 32$, $64 \times 64$ operands since with bigger
block sizes, the operands do not fit in L1 cache. Several testcases
are considered and detailed.

>>>>

\subsubsection{Decoding}
In Figs.~\ref{fig:dec_ene_rasp1_gen_gf2}, \ref{fig:dec_ene_rasp1_gen_gf256},
\ref{fig:dec_ene_rasp1_packet_gf2} and \ref{fig:dec_ene_rasp1_packet_gf256} 
we show the encoding energy per bit consumption for the \ac{Raspi} 1.
Again, we notice very similar behavior and trends as previously
reviewed for the encoding energy per bit expenditure. In this case,
we focus on performance among the coding schemes since the behavior 
and trends were previously explained for the encoding case. Later,
we introduce the decoding energy results for the \ac{Raspi} 2 doing
relevant comparisons with the \ac{Raspi} 1.
%
\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_generation_size_Rasp_Binary_decoder_1600.eps}
        \caption[]%
        {{\small Energy per bit vs. Generation size for $q = 2$}}
        \label{fig:dec_ene_rasp1_gen_gf2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_generation_size_Rasp_Binary8_decoder_1600.eps}
        \caption[]%
        {{\small Energy per bit vs. Generation size for $q = 2^8$}}
        \label{fig:dec_ene_rasp1_gen_gf256}
    \end{subfigure}
    \vskip\baselineskip
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_symbol_size_Rasp_Binary_decoder_128.eps}
        \caption[]%
        {{\small Energy per bit vs. Packet size for $q=2,\ g=128$}}
        \label{fig:dec_ene_rasp1_packet_gf2}
    \end{subfigure}
    \quad
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_symbol_size_Rasp_Binary8_decoder_128.eps}
        \caption[]%
        {{\small Energy per bit vs. Packet size for $q=2^8,\ g=128$}}
        \label{fig:dec_ene_rasp1_packet_gf256}
    \end{subfigure}
    \caption[]
    {\small Decoder energy measurements for the \ac{Raspi} 1}
    \label{fig:dec_ene_rasp1}
\end{figure*}
%
Some differences occurs due to nature of decoding. In this situation,
the reception of \ac{l.d.} coded packets just increases the decoding
delay, therefore reducing the performance of some coding schemes
in terms of the energy per bit consumption. For example, we notice
that using \ac{SRLNC} with $d = 0.02$ outperforms \ac{TSNC} with
$C = 0$ and $e = 16$, for most of the cases in the variable generation
size curves and in all the cases of variable packet size curves of
Fig.~\ref{fig:dec_ene_rasp1}. This is a clear scenario where the decoding
delay is energy-wise susceptible to the transmissions of \ac{l.d.}
coded packets. With the \ac{Raspi} 1, decoding energies per processed
bit of 2 nJ or similar are possible. 
%
\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_generation_size_Rasp_v2_Binary_decoder_1600.eps}
        \caption[]%
        {{\small Energy per bit vs. Generation size for $q = 2$}}
        \label{fig:dec_ene_rasp2_gen_gf2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_generation_size_Rasp_v2_Binary8_decoder_1600.eps}
        \caption[]%
        {{\small Energy per bit vs. Generation size for $q = 2^8$}}
        \label{fig:dec_ene_rasp2_gen_gf256}
    \end{subfigure}
    \vskip\baselineskip
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_symbol_size_Rasp_v2_Binary_decoder_128.eps}
        \caption[]%
        {{\small Energy per bit vs. Packet size for $q=2,\ g=128$}}
        \label{fig:dec_ene_rasp2_packet_gf2}
    \end{subfigure}
    \quad
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.05\textwidth]{images/06_06_2016/energy_per_bit_vs_symbol_size_Rasp_v2_Binary8_decoder_128.eps}
        \caption[]%
        {{\small Energy per bit vs. Packet size for $q=2^8,\ g=128$}}
        \label{fig:dec_ene_rasp2_packet_gf256}
    \end{subfigure}
    \caption[]
    {\small Decoder energy measurements for the \ac{Raspi} 2}
    \label{fig:dec_ene_rasp2}
\end{figure*}
%
Finally, in Figs.~\ref{fig:dec_ene_rasp2_gen_gf2},
\ref{fig:dec_ene_rasp2_gen_gf256}, \ref{fig:dec_ene_rasp2_packet_gf2}
and \ref{fig:dec_ene_rasp2_packet_gf256}; we introduce the decoding energy
per bit consumption for the \ac{Raspi} 2. Here, we obtain a reduction
of an order of magnitude in energy per processed bit due to the speed
of the \ac{Raspi} 2. For example, it can be seen that for the binary field
with $g = 16$ packets, we achieve a decoding energy consumption per bit 
processed close to 0.1 nJ in practical systems.
%
\subsection{Multicore Network Coding}
\label{subs:multicore-network-coding}

To review the performance of \ac{NC} in a multicore using the \ac{Raspi},
the authors implemented the algorithm described in
Section~\ref{sub:implementation-multicore} on the \ac{Raspi} 2 model,
which features four ARMv7 cores in a Broadcom BCM2836 \ac{SOC}
with a 900 MHz clock. Each core has a 32 KiB L1 data cache and 32 KiB
L1 instruction cache. The cores share a 512 KiB L2 cache. All the
measured results, including the baseline results, were obtained with
NEON-enabled code adapted from the Fifi library [\textbf{Fifi reference}].
The \ac{Raspi} 2 has a NEON extension instruction set which provides
an 128-bit \ac{SIMD} instructions that speed the computations.
Figures~\ref{enc_dec1024}, \ref{enc_dec128} and
\ref{enc_dec16} show the encoding and decoding goodput in MB per
second for different generation sizes, $g = [1024, 128, 16]$
respectively. The size of each coded packet was fixed to $1536$~bytes
since that is the typical size of an Ethernet frame. The blocked operations
were performed dividing the matrices in squared sub-blocks of
$16,\ 32\ ,\ 64,\ldots,\ 1024$ operands (words in the Galois field) in
height and width. The figures show only block sizes of
$16 \times 16$, $32 \times 32$, $64 \times 64$ operands since with bigger
block sizes, the operands do not fit in L1 cache. Several testcases
are considered and detailed.
